Lab 11 - Missing Data and Imputation

### 2023-04-05 Lab 11 Missing data/Lab11_MissingData.Rmd
Add files via upload

#lets copy this df and then add some missingness
data_miss <- data_clean
data_miss[6:27,2] <- rep(NA,2)
data_miss[102:119,4] <- rep(NA,2)
data_miss[35:50,3] <- rep(NA,2)
summary(data_miss) #check out those *~* NAs ~*~

>>>>

#lets copy this df and then add some missingness
data_miss <- data_clean
data_miss[52:59,1] <- rep(NA,2)
data_miss[6:27,2] <- rep(NA,2)
data_miss[102:119,4] <- rep(NA,2)
data_miss[35:50,3] <- rep(NA,2)
summary(data_miss) #check out those *~* NAs ~*~
